### 2020-03-06 draft_ABP.tex
update a commit
Update draft_ABP.tex

In the last subsection, we have seen that any $n$-dimensional generalized 
permutahedron can be constructed by a Minkowski sum of some simplices labeled by
subsets of $[0,n]$. For a simplex labeled by a subset $I$, it can be realized as the 
Newton Polytope of the linear polynomial $x_I=\sum_{i\in I}x_i$. Therefore, we can
write down a natrual stringy canonical form for the generalized permutahedron 
$\mathscr P$
\[
	\mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n+1}_+}
	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
\]
where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
$\sum_{I\in\mathscr P}S_I = 0$.

@@

(Zhenjie: what are the facets of general permutahedra?  I believe they are known.)

>>>>

In the last subsection, we have seen that any $n$-dimensional generalized 
permutahedron can be constructed by a Minkowski sum of some simplices labeled by
subsets of $[0,n]$. For a simplex labeled by a subset $I$, 
it is natrual to associate the linear polynomial $x_I=\sum_{i\in I}x_i$ whose Newton polytope is the corresponding simplex. Therefore, we can write down a natrual stringy canonical form for the generalized permutahedron with the building set 
$\mathscr P$
\[
	\mathcal I_{\mathscr P}(\{S_I\})=\int_{\mathbb R^{n}_+}
	\frac{\prod_{i=0}^n \mathrm{d}\log x_i}
	{\operatorname{GL}(1)_+}\prod_{I\in\mathscr P}x_I^{\alpha' S_I},
\]
where the global $\operatorname{GL}(1)_+$ redundance $x_i\mapsto a x_i$ require that 
$\sum_{I\in\mathscr P}S_I = 0$.

@@

(Zhenjie: Are facets of $\mathscr A$ associated with $J$ just the $F_J$ of $\mathscr P_n$ after setting all $S_I=0$ for $I\not\in \mathscr A$? How to prove it?)
